\documentclass{article}
\usepackage{amsmath, amsthm, amsfonts}
\begin{document}
To calculate the integral of sin(x)/x, we can use the technique of integration by parts. The formula for integration by parts is given by:

\[
\int u \, dv = uv - \int v \, du
\]

where u and v are functions of x.

In this case, we can choose u = sin(x) and dv = \frac{1}{x} \, dx. Taking the derivatives and integrals, we have:

du = \cos(x) \, dx
v = \int \frac{1}{x} \, dx = \ln|x|

Now we can substitute these values into the integration by parts formula:

\[
\int \frac{\sin(x)}{x} \, dx = \int u \, dv = uv - \int v \, du = \sin(x) \ln|x| - \int \ln|x| \cos(x) \, dx
\]

To evaluate the remaining integral, we can use integration by parts again. Let's choose u = \ln|x| and dv = \cos(x) \, dx. Taking the derivatives and integrals, we have:

du = \frac{1}{x} \, dx
v = \int \cos(x) \, dx = \sin(x)

Substituting these values into the integration by parts formula, we get:

\[
\int \ln|x| \cos(x) \, dx = \ln|x| \sin(x) - \int \sin(x) \frac{1}{x} \, dx
\]

Now we have another integral to evaluate, but this time it's simpler. The integral of \frac{\sin(x)}{x} \, dx is a well-known integral called the sine integral, denoted as Si(x). Therefore, we have:

\[
\int \sin(x) \frac{1}{x} \, dx = Si(x)
\]

Substituting this back into the previous equation, we get:

\[
\int \ln|x| \cos(x) \, dx = \ln|x| \sin(x) - Si(x)
\]

Finally, substituting this result back into the original equation, we have:

\[
\int \frac{\sin(x)}{x} \, dx = \sin(x) \ln|x| - \ln|x| \sin(x) + Si(x)
\]

Simplifying this expression, we get:

\[
\int \frac{\sin(x)}{x} \, dx = Si(x)
\]

Therefore, the integral of sin(x)/x is Si(x).

To validate the correctness of the solution, we can differentiate the result and check if it gives us back the original function. Differentiating Si(x) with respect to x gives us:

\[
\frac{d}{dx} Si(x) = \frac{\sin(x)}{x}
\]
\end{document}